Evolution of ORM Systems: Formal Foundations

### 2013-01-09 doc/description.tex
fixed associated(l,a) function for class

\begin{align*}
  \mathbf{Application} = < Class* > \\ 
  \mathbf{app} : Class* \rightarrow  Application \\ \\
  \mathbf{classes} : Application \rightarrow Class* \\
  classes(app(cs)) = cs  \\\\
  \mathbf{class} : Label \times Application \rightarrow Class   \\ 
  class(l, a) = c, c \in classes(a) \wedge name(c) = l \\ \\
  l \in Label, a = Application, cs \in Class* 
  \\ \\
  \mathbf{associated} :  Label \times Application \rightarrow Boolean \\
\end{align*}

\paragraph{Class} represents a basic structural concept in the application model. It has a unique name, one or more properties and a class can be associated to other classes in the application. 
\begin{align*}
	\mathbf{Class} = <label, Property*, Association*> \\
	\mathbf{cl} : Label \times Property* \times Association* \rightarrow Class \\\\
% TODO association has to be only to self (all associated has to exists)
	\mathbf{name} : Class \rightarrow Label \\
	name(cl(l, props, assocs)) = l \\ \\
	\mathbf{properties} : Class \rightarrow Property* \\
	properties(cl(l, props, assocs)) = props \\ \\
	\mathbf{primitiveProperties} : Class \rightarrow Property* \\	primitiveProperties(cl(l, props, assocs)) = props', \\ props' \subset props,  \forall p \in props' : cardinality(p) \leq 1 \\ \\
	\mathbf{collectionProperties} : Class \rightarrow Property* \\	collectionProperties(cl(l, props, assocs)) = props', \\ props' \subset props, \forall p \in props' : cardinality(p) > 1 \\ \\
	\mathbf{associations} : Class \rightarrow Association* \\	associations(cl(l, props, assocs)) = assocs \\ \\
l \in Label, props \in Properties, assocs \in Associations
\end{align*}

>>>>

\begin{align*}
  \mathbf{Application} = < Class* > \\ 
  \mathbf{app} : Class* \rightarrow  Application \\ \\
  \mathbf{classes} : Application \rightarrow Class* \\
  classes(app(cs)) = cs  \\\\
  \mathbf{class} : Label \times Application \rightarrow Class   \\ 
  class(l, a) = c, c \in classes(a) \wedge name(c) = l \\ \\
  l \in Label, a = Application, cs = Class* 
\end{align*}

\paragraph{Class} represents a basic structural concept in the application model. It has a unique name, one or more properties and a class can be associated to other classes in the application. 
\begin{align*}
	\mathbf{Class} = <label, Property*, Association*> \\
	\mathbf{cl} : Label \times Property* \times Association* \rightarrow Class \\\\
% TODO association has to be only to self (all associated has to exists)
	\mathbf{name} : Class \rightarrow Label \\
	name(cl(l, props, assocs)) = l \\ \\
	\mathbf{properties} : Class \rightarrow Property* \\
	properties(cl(l, props, assocs)) = props \\ \\
	\mathbf{primitiveProperties} : Class \rightarrow Property* \\	primitiveProperties(cl(l, props, assocs)) = props', \\ props' \subset props,  \forall p \in props' : cardinality(p) \leq 1 \\ \\
	\mathbf{collectionProperties} : Class \rightarrow Property* \\	collectionProperties(cl(l, props, assocs)) = props', \\ props' \subset props, \forall p \in props' : cardinality(p) > 1 \\ \\
	\mathbf{associations} : Class \rightarrow Association* \\	associations(cl(l, props, assocs)) = assocs \\ \\
	\mathbf{associated} :  Label \times Application \rightarrow Boolean \\
  	associated(l,a) = \begin{cases}
  		\inference{\exists c \in classes(a) \wedge \exists e \in associations(c) : reference(e) = l
  	}{ true } \\
 		false
 	\end{cases} \\ \\
	l \in Label, props = Property*, assocs = Association*, a = Application
\end{align*}
